\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach

### 2021-08-08 presentationESSLLI21/presentationESSLLI.Rmd
final details

- Gender-direction: insufficient indicator of bias [@Gonen2019lipstick]

- Use of analogies: unreliable [@Nissim2020fair]

- High sensitivity to irrelevant factors [@zhang2020robustness]

@@

What values are sufficient for the presence of bias and what differences are sign of real improvement? Low $p$-values are not high effect indicators!

We compare HPDIs.

@@

Suppose all similarities for two classes are randomly drawn from the same distribution, $\mathsf{Normal}(0,.05)$, you still can get really high WEAT!

@@

@@

   \begin{itemize}
   \item Male attributes strong co-occurrence with female attributes
   \item Sometimes different is stronger than associated
   \item Almost no overlap with control groups
   \end{itemize}
   \end{minipage}
\end{figure}

>>>>

- Gender-direction: insufficient indicator of
    bias  \footnotesize  [@Gonen2019lipstick]

- Use of analogies: unreliable \footnotesize  [@Nissim2020fair] \normalsize

- High sensitivity to irrelevant factors \footnotesize  [@zhang2020robustness] \normalsize

@@

- What values are sufficient for the presence of bias and what differences are sign of real improvement?

- Low $p$-values are not high effect indicators!

- We compare HPDIs.

@@

Suppose all similarities for two classes are randomly drawn from the same distribution, $\mathsf{Normal}(\mu = 0, \sigma = .05)$, you still can get a really high WEAT!

@@

\vspace{-2mm}

@@

   \begin{itemize}
   \item Male attributes: strong co-occurrence with female attributes
   \item Sometimes \textsf{different} is closer than \textsf{associated}
   \item Almost no overlap with control groups
   \end{itemize}
   \end{minipage}
\end{figure}
